---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BSCB

<!-- badges: start -->
<!-- badges: end -->

## Title of the manuscript: 

Bayesian Simultaneous Credible Bands for Polynomial Regression

The goal of BSCB is to quantify the uncertainty in an unknown regression functions over a given continuous range. The method consists of 
This manuscript proposes a novel framework for constructing a $(1-\alpha)$ two-sided exact BSCB for the polynomial model over the given covariate interval $(a,b)$. Three approaches have been developed based on (i) the normal-gamma conjugate prior, (ii) the independent Jeffreys prior for objective inference, and (iii) the non-conjugate prior implemented by the Hamiltonian Monte Carlo (HMC) method. 



## Authors:

Fei Yang, Yang Han, and Wei Liu

## Configurations:
* R version 4.4.2 (2024-10-31)
* Platform: aarch64-apple-darwin20
* Running under: macOS Ventura 13.7.8
* Running Environment: The Computational Shared Facility (a High-Performance Computing cluster at the University of Manchester) 

## Execution:
To use the codes for reproducing numerical results, tables and figures given in the paper and its supplement, please follow the instructions below.

## Main Manuscript

1. Simulation Study – Section 4
	* Reproduce Table 1 in the manuscript:
	  * Use the file [‘Run_Poly_p=2_doParallel.R’](https://github.com/fannyyang73/BSCB/tree/main/inst/paper/simulations/Example_1/p%3D2/code_p%3D2/Run_Poly_p=2_doParallel.R) to reproduce results for p=2.
	  * Use the file [‘Run_Poly_p=3_doParallel.R’](https://github.com/fannyyang73/BSCB/tree/main/inst/paper/simulations/Example_1/p%3D3/code_p%3D3/Run_Poly_p=3_doParallel.R) to reproduce results for p=3.
	  

<!-- 1. Illustrative Example - Section 4 -->
<!-- 	* Reproduce Table 3, Figure 3 and the numerical results in the manuscript: -->
<!-- 	  * Use the file ‘Real_data_example.R’. -->

<!-- 2. Simulation Study – Section 3 -->
<!-- 	* Reproduce Figure 2 and Table 2 in the manuscript: -->
<!-- 	  * Use the file ‘Simulation_study.R’. -->
<!-- 	  * Input the values of confl ($1-\alpha$), Cgamma ($\gamma$), $n$ and $s$ to compute the values of critical constants $c$ for symmetric SCBs and $(c_1,c_2)$ for asymmetric SCBs, and $r$-ratios. -->

``` r
# install.packages("pak")
pak::pak("fannyyang73/BSCB")
```

## Supplementary Materials

3. Computational Costs
	* Reproduce Tables 1-2 in the supplementary material:
	  * Use the file ‘Computational_cost_supple.R’.
	  
4. Additional Simulation Results 
	* Reproduce Tables 3-4 in the supplementary material:
	  * Use the file ‘Simulation_study_supple.R’.
	  * Input the values of confl ($1-\alpha$), Cgamma ($\gamma$), $n$ and $s$ to compute the values of critical constants $c$ for symmetric SCBs and $(c_1,c_2)$ for asymmetric SCBs, and $r$-ratios.



```{r example}
#library(BSCB)
## basic example code
```

## R package

A full demo for how to use the R package BSCB is provided in [here](https://github.com/fannyyang73/BSCB/tree/main/demo/BSCB_demo.Rmd).

You can install the development version of BSCB from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fannyyang73/BSCB")
```




