---
title: "BSCB_demo"
output: html_document
date: "2026-04-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bayesian simultaneous credible bands for the polynomial model

## Overview

This demo illustrates how to use the **BSCB** package to construct and
evaluate Bayesian simultaneous credible bands (BSCB) and Bayesian pointwise
credible bands (BPCB) for polynomial regression. Three methods are demonstrated:

- **BSCB-C**: BSCB under the Normal-Gamma conjugate prior
- **BSCB-J**: BSCB under the independent Jeffreys prior
- **BPCB-J**: BPCB under the independent Jeffreys prior


```{r}
library(BSCB)
```

## 1. Simulate Data

We simulate data from a quadratic regression model
$Y_i = \theta_0 + \theta_1 x_i + \theta_2 x_i^2 + \varepsilon_i$,
where $\varepsilon_i \sim N(0, \sigma^2)$.

```{r}
# Simulate data from a quadratic model
set.seed(123)
n <- 50
x <- seq(-0.5, 0.5, length.out = n)
X <- cbind(1, x, x^2)
theta_true <- c(-6, -3, 0.25)
Y <- X %*% theta_true + rnorm(n, sd = 0.2)
```

## 2. Construct the Bands

### BSCB-C: BSCB under the Normal-Gamma conjugate prior

The Normal-Gamma conjugate prior supports three hyperparameter specifications:
`"empirical"` (empirical Bayes), `"unit_info"` (unit-information prior), and
`"g_prior"` (Zellner's g-prior). The critical constant $\lambda$ is estimated
via $L = 500{,}000$ Monte Carlo draws.

```{r}
# --- BSCB-C: Bayesian simultaneous credible bands under the Normal-Gamma conjugate prior ---
fit_c <- compute_bscb_conjugate(
  X              = X,
  Y              = Y,
  alpha          = 0.05,
  a              = -0.5,
  b              =  0.5,
  L              = 500000,
  theta_true     = theta_true,
  hyperparameter = "g_prior",   # "empirical", "unit_info", or "g_prior"
  optimize_type  = "P"          # "P" = polyroot (recommended)
)

cat("Critical constant (BSCB-C):", fit_c$lambda, "\n")
cat("Posterior mean of theta:\n")
print(round(fit_c$mu_star, 4))
```

### BSCB-I-J: BSCB under the independent Jeffreys prior

BSCB-I-J is equivalent to the FSCB in Liu et al.(2008) for finite sample sizes.
```{r}
# --- BSCB-I-J: Bayesian simultaneous credible bands under the Independent Jeffreys prior ---
fit_j <- compute_bscb_ind_jeffreys(
  X     = X,
  Y     = Y,
  alpha = 0.05,
  a     = -0.5,
  b     =  0.5,
  theta_true     = theta_true,
  L     = 500000
)
cat("Critical constant (BSCB-J):", fit_j$lambda, "\n")
```

### BPCB-I-J: BPCB under the independent Jeffreys prior

BPCB-I-J is constructed by connecting confidence intervals at each individual points in the covariate domain. It's also equivalent to the FPCB.
```{r}
# --- BPCB-I-J: Bayesian pointwise credible bands under the Independent Jeffreys prior ---
fit_p <- compute_bpcb_ind_jeffreys(
  X     = X,
  Y     = Y,
  alpha = 0.05,
  a     = -0.5,
  b     =  0.5,
  theta_true     = theta_true
)

```

## 3. Evaluate Bands over a Grid and Plot

```{r}
library(ggplot2)
x_seq  <- seq(-0.5, 0.5, length.out = 500)
y_true <- as.numeric(cbind(1, x_seq, x_seq^2) %*% theta_true)
df_obs <- data.frame(x = x, Y = as.numeric(Y))

# Collect all band boundaries into a single data frame
df_bands <- data.frame(
  x       = rep(x_seq, 3),
  lower   = c(as.numeric(fit_c$lower_bound(x_seq)),
              as.numeric(fit_j$lower_bound(x_seq)),
              as.numeric(fit_p$lower_bound(x_seq))),
  upper   = c(as.numeric(fit_c$upper_bound(x_seq)),
              as.numeric(fit_j$upper_bound(x_seq)),
              as.numeric(fit_p$upper_bound(x_seq))),
  method  = rep(c("BSCB-C-G",
                  "BSCB-I-J",
                  "BPCB-I-J"),
                each = length(x_seq))
)

df_true <- data.frame(x = x_seq, y = y_true)

# Colour palette (Wong 2011, colourblind-friendly)
band_colours <- c(
  "BSCB-C-G"         = "#4DAF4A",
  "BSCB-I-J" = "#E41A1C",
  "BPCB-I-J" = "#377EB8"
)

band_linetypes <- c(
  "BSCB-C-G"         = "dashed",
  "BSCB-I-J" = "dashed",
  "BPCB-I-J" = "dotted"
)

ggplot() +
  # Shaded credible regions
  geom_ribbon(
    data    = df_bands,
    mapping = aes(x = x, ymin = lower, ymax = upper,
                  fill = method),
    alpha   = 0.10
  ) +
  # Band boundaries
  geom_line(
    data    = df_bands,
    mapping = aes(x = x, y = lower,
                  colour   = method,
                  linetype = method),
    linewidth = 0.8
  ) +
  geom_line(
    data    = df_bands,
    mapping = aes(x = x, y = upper,
                  colour   = method,
                  linetype = method),
    linewidth = 0.8
  ) +
  # True regression curve
  geom_line(
    data      = df_true,
    mapping   = aes(x = x, y = y),
    colour    = "navyblue",
    linewidth = 0.7,
    linetype  = "solid"
  ) +
  # Observed data
  geom_point(
    data    = df_obs,
    mapping = aes(x = x, y = Y),
    colour  = "gray50",
    size    = 1.5
  ) +
  scale_colour_manual(values = band_colours, name = "Method") +
  scale_fill_manual(values   = band_colours, name = "Method") +
  scale_linetype_manual(values = band_linetypes, name = "Method") +
  labs(
    title = "95% Bayesian Credible Bands for Quadratic Regression",
    x     = "x",
    y     = "y"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

## 4. Evaluate Coverage

### Empirical Simultaneous Coverage Rate (ESCR)

`coverage_ESCR()` returns 1 if the true regression function lies within the
band at all points in $[a, b]$, and 0 otherwise.

```{r}
escr_c <- coverage_ESCR(fit_c, optimize_type = "P", verbose = TRUE)
escr_j <- coverage_ESCR(fit_j, optimize_type = "P", verbose = TRUE)
escr_p <- coverage_ESCR(fit_p, optimize_type = "P", verbose = TRUE)

cat("ESCR (BSCB-C):", escr_c, "\n")
cat("ESCR (BSCB-I-J):", escr_j, "\n")
cat("ESCR (BPCB-I-J):", escr_p, "\n")
```

### Posterior Simultaneous Coverage Probability (PSCP)

`coverage_PSCP()` estimates the proportion of posterior draws for which
$\sup_{x \in [a,b]} T(x) \leq \lambda$.

```{r}
pscp_c <- coverage_PSCP(fit_c, draw_num = 10000,
                         optimize_type = "P", verbose = TRUE)
pscp_j <- coverage_PSCP(fit_j, draw_num = 10000,
                         optimize_type = "P", verbose = TRUE)
pscp_p <- coverage_PSCP(fit_p, draw_num = 10000,
                         optimize_type = "P", verbose = TRUE)

cat("PSCP (BSCB-C):", round(pscp_c, 4), "\n")
cat("PSCP (BSCB-I-J):", round(pscp_j, 4), "\n")
cat("PSCP (BPCB-I-J):", round(pscp_p, 4), "\n")
```

### Summary Table

```{r}
summary_tab <- data.frame(
  Method   = c("BSCB-C-G", "BSCB-I-J"),
  Lambda   = round(c(fit_c$lambda, fit_j$lambda), 4),
  ESCR     = c(escr_c, escr_j),
  PSCP     = round(c(pscp_c, pscp_j), 4)
)
knitr::kable(summary_tab, caption = "Coverage summary for one simulated dataset")
```
